Figures and Tables

### 2021-02-08 paper/figures_tables.Rmd
Edits to captions

## Seed dispersal distances and aggregation
#### Figure 4. Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates. **A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates. Each individual line represents the dispersal kernel generated by each individual animal. The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group. **B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models. **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models. The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1. *Is there more comparison I should mention here? Like, how the larger values are more abundant in the individual model?*

@@

## Long distance dispersal

@@

## Weibull seed dispersal kernel

@@

## Generalized Pareto tail distribution for seed dispersal
Actually, do use the thresholds from the diagnostic plots. These are the parameters with those thresholds.

@@

@@

### Probabilities

@@

## Figures for seed dispersal kernels and comparison to the fit
Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family. The reason for this, is that when you sample seedlings or seed dispersal distances, you don't know which animal moved which, you just get plant level information and distance to the parent tree. So, now, we visualize the seed dispersal kernels for each of the three models, without considering the variation contributed to the kernel by each individual.

```{r}
# Fit to the data?

@@

```{r fig.height=9, fig.width=6}
# Fit to the data?

@@

>>>>

## Results
#### Figure 4. Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates. **A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates. Each individual line represents the dispersal kernel generated by each individual animal. The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group. **B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models. **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models. The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1. *Is there more comparison I should mention here? Like, how the larger values are more abundant in the individual model?*

@@

@@

### Weibull seed dispersal kernel

#### Table 2. Parameter estimates for seed dispersal kernels on each of the simulation models using a Weibull distribution to characterize the kernel. Parameter values are reported with their standard deviations in parentheses.

@@

#### Figure 5. Kernels produced from Weibull functions using the estimated parameters for each of the simulated models. Inset shows a zoom to the tail of the distribution emphasizing the variation in long-distance dispersal events described by each of the models. Red line is used for reference as the original 500m threshold to describe long-distance dispersal events in previous studies. We observe fatter tails for the model with individual variation in animal movement, followed by family level variation, and a thinner tail for the null simulation model with no variation in animal movement.

```{r}
dispersal_data %>% 
  ggplot(aes(x = dispersal)) +
  # stat_density(aes(linetype = model), geom = "line", position = "identity") +
  geom_function(aes(linetype = "Null"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
  geom_function(aes(linetype = "Individual"),
                fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
  geom_function(aes(linetype = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
  geom_vline(xintercept = 500, color = "red") +
  theme_half_open(10) +
  labs(y = "Density", x = "Seed dispersal (m)") +
  theme(legend.position = c(0.8, 0.8),
        legend.title = element_blank()) -> dispersal_data_plot

plot.with.inset
```

## Generalized Pareto tail distribution for seed dispersal

#### Table 3. Threshold values and parameter estimates for generalized Pareto distribution fits, and associated standard error for parameter estimates.

@@

#### Figure 6.

@@

#### Table 4. Probability of long-distance dispersal events for the three models following a generalized Pareto distribution.

@@

<!-- ## Figures for seed dispersal kernels and comparison to the fit -->
<!-- Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family. The reason for this, is that when you sample seedlings or seed dispersal distances, you don't know which animal moved which, you just get plant level information and distance to the parent tree. So, now, we visualize the seed dispersal kernels for each of the three models, without considering the variation contributed to the kernel by each individual. -->

```{r eval = FALSE}
# Fit to the data?

@@

```{r eval=FALSE, fig.height=9, fig.width=6}
# Fit to the data?

@@

### Variation in kernels produced by individual birds in each of the three models

```{r}
dispersal_data %>% 
  dplyr::filter(model == "Null") %>% 
  ggplot(., aes(x = dispersal)) +
  facet_wrap(~id) +
  geom_density() +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(title = "Null simulation model", y = "Density", x = "Seed dispersal (m)")

dispersal_data %>% 
  dplyr::filter(model == "Individual") %>% 
  ggplot(., aes(x = dispersal)) +
  facet_wrap(~id) +
  geom_density() +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(title = "Individual simulation model", y = "Density", x = "Seed dispersal (m)")

dispersal_data %>% 
  dplyr::filter(model == "Family") %>% 
  ggplot(., aes(x = dispersal)) +
  facet_wrap(~id) +
  geom_density() +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(title = "Family simulation model", y = "Density", x = "Seed dispersal (m)")
